---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-",
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```
# snaputils

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/snaputils.svg?branch=master)](https://travis-ci.org/leonawicz/snaputils)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/snaputils?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/snaputils)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/snaputils/master.svg)](https://codecov.io/github/leonawicz/snaputils?branch=master)

`snaputils` contains utilities for Shiny app development.
The package inherits primarily from `apputils`, which contains common utility functions, settings and references for use across multiple Shiny apps.
It also imports `maputils`. As the name suggests, unlike the other two packages, `snaputils` is specific to a SNAP context. 
All three packages are satellite members of the SNAPverse collection of R packages.

## Installation

You can install snaputils from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/snaputils")
```
